Meta-analysis

### 2019-07-17 05_MetaAnalysis.Rmd
Added formula to calculate standard deviation from the LSD. Needs to be checked

```{r}
PM_MB_means <- read.csv("data/1902 powdery mildew-Mungbean - Collated means.csv")
str(PM_MB_means)
```

@@

@@

>>>>

```{r Meta_dataImport}
PM_MB_means <- read.csv("data/1902 powdery mildew-Mungbean - Collated means.csv")

str(PM_MB_means)
```

@@

PM_MB_means %>%
   filter(Fungicide == "Tebeconazole",
          row_spacing == 0.75)

@@

```{r LSD_2_SD}
# Formula and modifications based off information found at https://www.statisticshowto.datasciencecentral.com/how-to-calculate-the-least-significant-difference-lsd/
colnames(PM_MB_means)

Tcrit <- 1.697  # 0.05 and DFw = 30 # T critical value for which there is significant difference between two groups
DFw <- sum(PM_MB_means[PM_MB_means$Trial_ref == "mung1112/02",]$Replicates) - 
   length(PM_MB_means[PM_MB_means$Trial_ref == "mung1112/02",]$Replicates) # degrees of freedom within groups
n.A <- PM_MB_means[PM_MB_means$Trial_ref == "mung1112/02",]$Replicates[1]
n.B <- PM_MB_means[PM_MB_means$Trial_ref == "mung1112/02",]$Replicates[1]
LSD <- PM_MB_means[PM_MB_means$Trial_ref == "mung1112/02",]$Yield_error[1]

# SSwithin <- #unknown
# MSW <- SSwithin / DFw # mean square within (SS within / DF within)

#  LSD = (Tcrit) * sqrt(MSW * (1/n.A + 1/n.B))
#  (LSD/Tcrit) = sqrt(MSW * (1/n.A + 1/n.B))
#  (LSD/Tcrit)^2 = MSW * (1/n.A + 1/n.B)
#  (LSD/Tcrit)^2/(1/n.A + 1/n.B) = MSW
MSW <- (LSD/Tcrit)^2/(1/n.A + 1/n.B)

SSquares <- MSW * DFw

Stdev <- sqrt(
   (1/(PM_MB_means[PM_MB_means$Trial_ref == "mung1112/02",]$Replicates[1] - 1)) * 
      SSquares)
